# 1.2.5 Exercises

Loading the packages

```{r}
library(tidyverse)
library(palmerpenguins)
library(ggthemes)
```

Loading the data

```{r}
pngs <- palmerpenguins::penguins
glimpse(pngs)
```

```{r 3: Make a scatterplot of bill_depth_mm vs. bill_length_mm. That is, make a scatterplot with bill_depth_mm on the y-axis and bill_length_mm on the x-axis. Describe the relationship between these two variablesm}

ggplot(pngs,
    # aesthetic on the global level, passed down to all subsequent geom layers
    mapping = aes(x = bill_length_mm, 
                  y = bill_depth_mm)) +
    # geometrical object that representa the data
    # each geom function can have own aesthetics
    # aesthetic mappings at the local level
    geom_point(mapping = aes(color = species,  
                             shape = species)) + 
    # new geometric object based on a linear model
    geom_smooth(method = "lm") +
    labs(
        title = "Bill length and Bill depth",
        subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
        x = "Bill length (mm)", 
        y = "Bill depth (mm)",
        color = "Species", 
        shape = "Species") +
    scale_color_colorblind()
```

```{r 4: What happens if you make a scatterplot of species vs. bill_depth_mm? What might be a better choice of geom?}
ggplot(
    data = pngs,
    # aesthetic on the global level, passed down to all subsequent geom layers
    mapping = aes(x = species, 
                  y = bill_depth_mm)) +
    # geometrical object that representa the data
    # each geom function can have own aesthetics
    # aesthetic mappings at the local level
    # geom_col(mapping = aes(color = species))\
    geom_point()

# Species is a categorical variable and a scatterplot of a categorical variable is not that useful 
```

```{r 5: Why does the following give an error and how would you fix it?}
# ggplot(data = penguins) + 
  # geom_point()
# no aesthetic mappings are provided
```

```{r 6: What does the na.rm argument do in geom_point()? What is the default value of the argument? Create a scatterplot where you successfully use this argument set to TRUE}
ggplot(data = penguins,
       aes(x = bill_depth_mm, y = bill_length_mm)) + 
    # Add the following caption to the plot you made in the previous exercise: Hint: Take a look at the documentation for labs()
    labs(title = "Data comes from the palmerpenguins package.") +
    # default is FALSE <- 
    geom_point(na.rm = TRUE)


```

```{r 7: Add the following caption to the plot you made in the previous exercise: Hint: Take a look at the documentation for labs()}
ggplot(data = penguins,
       aes(x = bill_depth_mm, y = bill_length_mm)) + 
    labs(title = "Data comes from the palmerpenguins package.") +
    # default is FALSE
    geom_point(na.rm = TRUE)
```

```{r 8: Recreate the following visualization. What aesthetic should bill_depth_mm be mapped to? And should it be mapped at the global level or at the geom level?}
ggplot(
    data = pngs,
    mapping = aes(
        x = flipper_length_mm, 
        y = body_mass_g)) +
    geom_point(aes(color = bill_depth_mm)) +
    geom_smooth()
```

```{r 9: Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.}
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, 
                y = body_mass_g,
                # aesthetic for global level?
                color = island)) +
  geom_point() +
  geom_smooth(se = FALSE)

ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g)) +
    # aesthetic for local level?
    geom_point(aes(color = island)) +
    geom_smooth(se = TRUE)
```

```{r 10: Will these two graphs look different? Why/why not?}
ggplot(
  data = penguins,
  # the aesthetic will be visible for both geoms
  mapping = aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() +
  geom_smooth()


ggplot() +
  geom_point(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_smooth(data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g),
    method = "lm")
```

# 1.4.3 Exercises

```{r 1: Make a bar plot of species of penguins, where you assign species to the y aesthetic. How is this plot different?}
ggplot(pngs, 
       aes(y = fct_infreq(species))) +
    geom_bar()
```


```{r 2: How are the following two plots different? Which aesthetic, color or fill, is more useful for changing the color of bars?}
ggplot(pngs,
       aes(x = fct_infreq(species))) +
    geom_bar(color = "red")

ggplot(pngs, 
       aes(x = fct_infreq(species))) +
    # fill is better for coloring the whole bar
    geom_bar(fill = "red")
```

```{r 4: Make a histogram of the carat variable in the diamonds dataset that is available when you load the tidyverse package}

ggplot(diamonds,
       aes(x = carat)) +
    geom_histogram(binwidth = 0.1)

```

# 1.5.5 Exercises

1: The mpg data frame that is bundled with the ggplot2 package contains 234 observations collected by the US Environmental Protection Agency on 38 car models. Which variables in mpg are categorical? Which variables are numerical? (Hint: Type ?mpg to read the documentation for the dataset.) How can you see this information when you run mpg?

```{r}
glimpse(mpg)
```

2: Make a scatterplot of hwy vs. displ using the mpg data frame. Next, map a third, numerical variable to color, then size, then both color and size, then shape. How do these aesthetics behave differently for categorical vs. numerical variables?

```{r}
ggplot(mpg, 
       aes(x = hwy,
           y = displ,
           color = cty)) +
    geom_point(aes(size = cty, shape = class))
```


Make a scatterplot of bill_depth_mm vs. bill_length_mm and color the points by species. What does adding coloring by species reveal about the relationship between these two variables? What about faceting by species?

```{r}
ggplot(pngs, 
       aes(x = bill_depth_mm,
           y = bill_length_mm)) +
    geom_point(aes(color = species)) +
    facet_wrap(~species)
```

```{r}
ggplot(
  data = penguins,
  mapping = aes(
    x = bill_length_mm, 
    y = bill_depth_mm, 
    shape = species,
    color = species)) +
  geom_point() +
  # both shape and color should be renamed!!!!
  labs(color = "Species",
       shape = "Species")
```

