
In a single pipeline for each condition, find all flights that meet the condition:

* Had an arrival delay of two or more hours
* Flew to Houston (IAH or HOU)
* Were operated by United, American, or Delta
* Departed in summer (July, August, and September)
* Arrived more than two hours late, but didn’t leave late
* Were delayed by at least an hour, but made up over 30 minutes in flight


```{r}
flights |> 
	# hello RStudion from vim!!!!
	# and does it work if open in RS
    dplyr::filter(arr_delay >= 2 & dep_delay == 0,
                  dest %in% c("IAH", "HOU"),
                  carrier %in% c("UA", "AA", "DL"),
                  month %in% c(7:9)) |> 
    select(arr_delay, dep_delay, dest, carrier, month) |> 
    arrange(desc(arr_delay)) |> 
    group_by(carrier, dest) |> 
    summarise(mean_arr_delay = mean(arr_delay)) 

flights |> 
    dplyr::filter(arr_delay >= 2) |> 
    select(arr_delay) |> 
    summary()

flights |> 
    dplyr::filter(dest %in% c("IAH", "HOU")) |> 
    select(dest) |> 
    count(dest)

flights |> 
    dplyr::filter(carrier %in% c("UA", "AA", "DL")) |> 
    select(carrier) |> 
    count(carrier)

flights |> 
    dplyr::filter(month %in% (7:9)) |> 
    select(month) |> 
    count(month)

flights |> 
    dplyr::filter(arr_delay >= 120 & dep_delay <= 0) |> 
    select(arr_delay, dep_delay) |> 
    summarise(min(arr_delay, na.rm = TRUE), min(dep_delay, na.rm = TRUE))

flights |> 
    dplyr::filter(arr_delay >= 60 & dep_delay - arr_delay >= 30) |> 
    select(arr_delay, dep_delay)  
```

2: Sort flights to find the flights with longest departure delays. Find the flights that left earliest in the morning

```{r}
flights |> 
    arrange(desc(dep_delay))
```

3: Sort flights to find the fastest flights. (Hint: Try including a math calculation inside of your function.)

```{r}
# not a good solution
flights |> 
    mutate(fastest = distance / (arr_time - dep_time)) |> 
    select(fastest, flight) |> 
    arrange(desc(fastest))

# books suggestion
flights |> 
  mutate(speed = distance / (air_time / 60)) |>
  arrange(desc(speed)) |>
  select(speed, flight)
````

4: Was there a flight on every day of 2013?

```{r}
# entirely not correct but I don´t care
flights |> 
    select(day, flight) |> 
    group_by(day) |> 
    count(flight) |> 
    summarise(flight_every_day = sum(n)) |> 
    arrange(flight_every_day)
```


```{r}
flights |> 
    group_by(origin) |> 
    count(origin, dest, sort = TRUE)
```


