imap kj <Esc>

Create a scatterplot of hwy vs. displ where the points are pink filled in triangles.

```{r}
mpg |> 
    ggplot(aes(hwy, displ)) +
    geom_point(color = "pink", shape = "triangle") +
    theme(legend.position = "none")
```

Why did the following code not result in a plot with blue points?

```{r}
# will not work
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy, color = "blue"))

ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy, color = "blue"))

# will not work
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = "blue"))

# will work
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(color = "blue")

# will work
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy), color = "blue")

# will kind of work 
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy), color = year)

# will work
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point(color = "blue")


```

What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

```{r}
# stroke is very hight here
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy), color = "blue", stroke = 100)
```

What happens if you map an aesthetic to something other than a variable name, like aes(color = displ \< 5)? Note, you’ll also need to specify x and y.

```{r}

```

```{r}

```
